MSF_Groupwork-NBA_shotlog

### 2016-10-11 MSFGroupwork-NBAHotHand.Rmd
add explanantion for dataset description

---
title: "MSF_Groupwork-NBA_shotlog" 
author: "Team_9"
output: html_document  ---
  title: "MSF_Groupwork-NBA_shotlog"
author: "Team_9"
output: html_document 
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Report produced by: Justin Leiendecker, Alexander Romanenko, Artmeis Tomadaki-Balomenou, Zijun Wei, Reza Widodo  
Date submitted: 16/10/2016

@@

###Introduction/Summary

The purpose of this report is to analyse a chosen dataset and to produce meaningful results using statistical and mathematical analysis. These analyses have been conducted using RStudio software. This report will focused on analysis of a number of areas, demonstrate how the analysis has been conducted, discusses theory used, demonstrate and evaluate produced results. In addition this report will highlight potential areas of future research.

The chosen dataset for this report is a summary of shots made during NBA season 2015-2016. The following areas of research have been selected:

#TO BE UPDATED when we know final areas
a. Hot Hand Theory (Artemis)
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate 
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i. Regression Analysis (Alex)

@@

#calculate correlation between defender distance and points made (2 or 3 points)
cor(point_type, distance)

@@

#calculate correlation between defender distance and shot result
cor(df[, "SHOT_RESULT"], df[, "CLOSE_DEF_DIS"])

@@

@@

```{r}
#Regression Analysis

df1$GAME_CLOCK <-as.numeric(df1$GAME_CLOCK)

df1$AWAY_TEAM <- as.character(df1$AWAY_TEAM)

linreg_fgm <-lm(FGM ~ LOCATION+W+FINAL_MARGIN+SHOT_NUMBER+ PERIOD+GAME_CLOCK+  SHOT_CLOCK+  DRIBBLES+ TOUCH_TIME+SHOT_DIST+PTS_TYPE+ CLOSEST_DEFENDER_PLAYER_ID + CLOSE_DEF_DIST+ player_id+ WINNER, df1 )

@@

linreg_fgm2 <-lm(FGM ~ FINAL_MARGIN+SHOT_NUMBER+ PERIOD +  SHOT_CLOCK+  DRIBBLES+ TOUCH_TIME+SHOT_DIST+PTS_TYPE+ CLOSE_DEF_DIST+ player_id, df1 )

summary(linreg_fgm2)

>>>>

---
title: "MSF_Groupwork-NBA_shotlog" 
author: "Team_9"
output:
  pdf_document: default
  html_document: default
---

@@

##Introduction
###What is your theme or research question?
    a. Hot Hand Theory (Artemis)
    b. Defender Proximity Analysis (Reza)
    c. Shot Clock Pressure  (Alex)
    d. Close Game Effect - Small Margin affecting the scoring rate 
    e. Home Advantage (Alex is working in this point)  
    f. Fatigue Effect (Quarter Heat Rate)  
    g. Shooting Percentage (James)
    h. Fatigue Effect (Number of Rest Day)  
    i. Regression Analysis (Alex)

##Theory
###What do you expect to find?
    a.

##Methods
I   Describe the dataset:

    Data on shots taken during the NBA 2014-2015 season for regular matches throughout the year. This comprehensive data comprise of 128,609 rows and 22 columns with 16 MB data size with only several value in a column is missing (shot clock). The column titles are generally self-explanatory. It has the following data:  
    1.  Match ID  
    2.  Match date  
    3.  Which team plays as home and away  
    4.  Match result  
    5.  Final score difference  
    6.  Every shots per game for each player  
    7.  Shot result whether it is success or not  
    8.  Shot attempt for 2 points or 3 points  
    9.  What is the game clock  
    10. How much time left for a shot (shot clock)  
    11. Who took the shot  
    12. Shot distance from basket  
    13. Who was the nearest defender  
    14. Distance from the nearest defender  
    The dataset is useful for evaluating who the best shooter is, who the best defender is, the hot-hand hypothesis, affect of home playing team, close game effect, shooting accuracy from best players, and defender distance effect on shooting accuracy. Data was taken from NBA's REST API provided by [Kaggle](https://www.kaggle.com/dansbecker/nba-shot-logs) and acquired at 30 September 2016.

@@

#calculate correlation between defender distance and points made (2 or 3 points)
cor.test(point_type, distance)

@@

#calculate correlation between defender distance and shot result
cor.test(df[, "SHOT_RESULT"], df[, "CLOSE_DEF_DIS"])

@@

#Calculate accuracy against defender distance
#Group the defender distance level

distance_level <- as.data.frame(table(factor(ClosestDefenderDistance)))
head(distance_level)

#Calculate how many times players scored in every defender distance
for (i in 1:nrow(distance_level)){
  distance_level[i, "SCORED"] <- sum(df[df[, "CLOSE_DEF_DIST"] == distance_level[i, "Var1"], "FGM"])
}

#Calculate shooting accuracy for each distance
distance_level$Accuracy <- round(distance_level$SCORED / distance_level$Freq, 2)

#Plotting the result
library(ggplot2)
ggplot(data = distance_level, aes(x = distance_level$Var1, y = distance_level$Accuracy)) +
  geom_point(aes(x = distance_level$Var1, y = distance_level$Accuracy))

#Calculate accuracy against shooting distance
#Group the shooting distance level
shooting_distance_level <- as.data.frame(table(factor(ShotDistance)))
head(shooting_distance_level)

#Calculate how many times players scored in every shooting distance
for (i in 1:nrow(shooting_distance_level)){
  shooting_distance_level[i, "SCORED"] <- sum(df[df[, "SHOT_DIST"] == shooting_distance_level[i, "Var1"], "FGM"])
}

#Calculate shooting accuracy for each distance
shooting_distance_level$Accuracy <- round(shooting_distance_level$SCORED / shooting_distance_level$Freq, 2)

#Plotting the result
library(ggplot2)
ggplot(data = shooting_distance_level, aes(x = shooting_distance_level$Var1, y = shooting_distance_level$Accuracy)) +
  geom_point(aes(x = shooting_distance_level$Var1, y = shooting_distance_level$Accuracy))
```

@@

```{r}
#Regression Analysis
colnames(df2)

linreg_fgm <-lm(FGM ~ GAME_ID1 + MATCHUP+LOCATION+W+FINAL_MARGIN+SHOT_NUMBER+ PERIOD+GAME_CLOCK+  SHOT_CLOCK+  DRIBBLES+ TOUCH_TIME+SHOT_DIST+PTS_TYPE+ SHOT_RESULT+ CLOSEST_DEFENDER + CLOSEST_DEFENDER_PLAYER_ID + CLOSE_DEF_DIST +PTS+player_name+ player_id+HOME_TEAM+AWAY_TEAM+WINNER, df2 )

@@

linreg_fgm2 <-lm(FGM ~ GAME_ID1 + MATCHUP+LOCATION+W+FINAL_MARGIN+SHOT_NUMBER+ PERIOD+GAME_CLOCK+  SHOT_CLOCK+  DRIBBLES+ TOUCH_TIME+SHOT_DIST+PTS_TYPE+ SHOT_RESULT+ CLOSEST_DEFENDER + CLOSEST_DEFENDER_PLAYER_ID + CLOSE_DEF_DIST +PTS+player_name+ player_id+HOME_TEAM+AWAY_TEAM+WINNER, df2 )
